%-------------------------
% Resume in Latex
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}
% \usepackage{fontawesome}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\LARGE Owen Q. Brooks} & \href{mailto:oqb23@drexel.edu}{oqb23@drexel.edu} \\%\faEnvelopeO\\
  \href{https://owen-brooks.github.io}{http://owen-brooks.github.io} & 240-472-8246 \\%\faPhone\\
  
\end{tabular*}


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Drexel University}{Philadelphia, PA}
      {Bachelor of Science in Computer Engineering;  GPA: 3.5}{Expected Graduation 2020}
      \resumeItemListStart
        \resumeItem{Relevant Coursework}
          {Algorithims, Data Analysis, Networking, Business Statistics, Embedded Systems, Discrete Math, Calculus I, II, Multivariate, Linear Algebra, Differential Equations, Digital Logic}
      \resumeItemListEnd
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Comcast}{West Chester, PA}
      {Data Engineering Co-op}{May 2018 - August 2018}
      \resumeItemListStart
      \resumeItem{Workflow Dashboard}
          {Designed and built full-stack Spring-Boot application allowing users to monitor data-transfer workflows. Leveraged 3rd party Java API to safely interact with automation software. }
        
        \resumeItem{Dev-Ops REST-API}
          {Automated and simplified access to application database by creating a REST API using Spring-Boot and JPA. Researched and implemented continuous deployment using Jenkins and Cloud-Foundry. Leveraged Spring Rest Docs to auto-generate scalable API documentation.
          }
          \resumeItem{Metadata Search App}
          {Increased data accessibility and understanding by developing a full-stack metadata-search application. Reformatted ElasticSearch database in order to improve query time and application scalability. }
          \resumeItem{Data Ingestion Automation}
          {Automated data transfer into Hadoop database with shell scripting. Researched and automated the conversion of shell scripts and utilities to Python. Validated ingested data with Hive.}
          
        \resumeItem{Employee Training}
          {Gave presentations to fellow Comcast employees on topics including: REST APIs, JPA, application frameworks, Jenkins, continuous deployment.}
      \resumeItemListEnd


    \resumeSubheading
      {G3 Technologies}{Mt. Airy, MD}
      {Software Engineering Co-op}{May 2017 - Sept 2017}
      \resumeItemListStart
      \resumeItem{Test Software}
          {Increased radio production by troubleshooting and fixing bugs found in Python applications. Restructured application interface in order to create a safe, standard user experience. }
        \resumeItem{Embedded Development}
          {Eliminated the need for micro-controllers in product development by creating signal-processing algorithms. Implemented and tested created algorithms using FTDI cables.}
        
        \resumeItem{RF Tuning And Production}
          {Exceeded monthly quotas for radio component production. Utilized a variety of mechanical and software tools to test and tune complex receivers, tuners, and their various modules}

      \resumeItemListEnd

    \resumeSubheading
      {Drexel NanoPhotonics Lab}{Philadelphia, PA}
      {Lab Assistant}{Sept 2017 - March 2018}
      \resumeItemListStart
       \resumeItem{Stage Automation}
          {Increased research efficiency by creating MATLAB programs to control and automate the use of optical stages. Eliminated previously needed calibration methods in the production of new imaging filters}
        \resumeItem{Optics Research}
          {Collaborated with researchers in the creation and testing of optical imaging filters. Utilized Class 3 lasers to ensure functionality of H-PDLC samples. Effectively collected and presented research data. }
       

      \resumeItemListEnd



  \resumeSubHeadingListEnd


%-----------PROJECTS-----------------
\section{Projects}
  \resumeSubHeadingListStart
    
      \resumeSubItem{Aether-Search}
      {Satellite search application developed for Starlight. Sensor data collected and organized using Python}
    \resumeSubItem{Craigslist-Car-Finder}
      {Flask web-scraping application built to search Craigslist car listings.}
      \resumeSubItem{Owen-brooks.github.io}
      {Personal website and blog with articles on various programming topics. Built with Jekyll.}
       \resumeSubItem{Drexel Design Project}
      {Robotics project using Lego hardware and Robot-C search algorithms. Competed and earned second place in object retrieval challenge.}
    
    
  \resumeSubHeadingListEnd
  


%
%-------- SKILLS------------
\section{Select Skills}
  \resumeSubHeadingListStart
  \resumeSubItem{Languages}
      {(proficient): Python, Java, SQL, Bash, MATLAB, HTML (familiar): C, JavaScript, R,  C++, VHDL}
    \resumeSubItem{Frameworks and Tools}
      {Git, Jenkins, Jira, Spring-Boot, Flask, Arduino, Hive, Oracle, MySQL, LabView, AutoCAD}
    \resumeSubItem{Test Equitment}
      {Signal Generator, Network Analyzer, Spectrum Analyzer, Oscilloscope}
  \resumeSubHeadingListEnd

%-----------extracurricular-----------------
\section{Extracurricular Activites}
  \resumeSubHeadingListStart
    \resumeSubItem{Drexel Men's Wrestling}
      {Team member and starter on nationally ranked Division I wrestling team.\textit{(2016 - Present)}}
    \resumeSubItem{Beat The Streets Philadelphia}
      {Peer mentor, tutor and coach for Philadelphia youth. Striving to teach principles of academic and athletic discipline, through the sport of wrestling.\textit{(2017 - Present)}}
  \resumeSubHeadingListEnd

%-------------------------------------------
\end{document}
